initial_analysis_notebook

### 2021-04-27 exploratory/notebook/initial_analysis/initial_analysis_notebook.Rmd
remove interactive plot

```{r}
library(plotly)
metadata <- read_tsv('../../../data/process/metadata_tidy.tsv',
		col_type = 'cccccDddddDcdddddcdl') 
shared <- read_tsv('../../../data/mothur/sample.final.0.03.subsample.shared',
		col_types = cols(.default = col_double(),
			Group = col_character())) %>% 
	mutate(Group = ifelse(grepl('_D|DA', Group), Group,
		gsub('D', '_D', Group)))
taxonomy <- read_tsv('../../../data/process/final.taxonomy.tidy.tsv',
                     col_types = cols(.default = col_character()))

@@

cowplot::plot_grid(lefse_plot, 
                   abundance_plot + 
                     geom_jitter(position = position_jitterdodge(dodge.width = 0.5), alpha = 0.25) + 
                     theme(axis.ticks.y = element_blank(),
                           axis.text.y = element_blank()), 
                   nrow = 1)

gg <- ggplotly(abundance_plot + geom_jitter(position = position_jitterdodge(dodge.width = 0.5)), tooltip = c('mouse_id'))
highlight(hide_legend(gg), on = "plotly_click", off = "plotly_doubleclick", 
           color = "black", selectize = T, opacityDim = .2,
           selected = attrs_selected(showlegend = F, marker = list(symbol = 'X')))
str(gg)
```

>>>>

```{r}

metadata <- read_tsv('../../../data/process/metadata_tidy.tsv',
		col_type = 'cccccDddddDcdddddcdl') 
shared <- read_tsv('../../../data/mothur/sample.final.0.03.subsample.shared',
		col_types = cols(.default = col_double(),
			Group = col_character())) %>% 
	mutate(Group = ifelse(grepl('_D|DA', Group), Group,
		gsub('D', '_D', Group)))
taxonomy <- read_tsv('../../../data/process/final.taxonomy.tidy.tsv',
                     col_types = cols(.default = col_character()))

@@

cowplot::plot_grid(lefse_plot, 
                   abundance_plot + 
                     geom_jitter(position = position_jitterdodge(dodge.width = 0.5), alpha = 0.25) + 
                     theme(axis.ticks.y = element_blank(),
                           axis.text.y = element_blank()), 
                   nrow = 1)
#library(plotly)
#gg <- ggplotly(abundance_plot + geom_jitter(position = position_jitterdodge(dodge.width = 0.5)), tooltip = c('mouse_id'))
#highlight(hide_legend(gg), on = "plotly_click", off = "plotly_doubleclick", 
#           color = "black", selectize = T, opacityDim = .2,
#           selected = attrs_selected(showlegend = F, marker = list(symbol = 'X')))

```
## Severe disease
```{r}
plot_lefse_data('severe_disease')
```
```
